|

### 2020-12-06 appendix/appendix.Rmd
edit fn2 in the appendix

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

>>>>

Our sample differs considerably in regards to research design. One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies. In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated. The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

### 2020-12-06 manuscript/article.Rmd
edit fn2 in the appendix

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. The
first studies that assessed the "law of $1/n$", as the theory is currently
known, mostly found a positive correlation between government spending and the
number of legislature seats, although the effect was sometimes limited to the
lower house [e.g., @baqir1999districts; @bradbury2001legislative;
@gilligan1995deviations]. However, recent studies have questioned the validity
of the theory. For instance, spending limits or strong executives may reduce
the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may
hold, wherein a higher number of legislators in small constituencies decrease
the overall public spending.

>>>>

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity.
Most of the early studies which assessed the "law of $1/n$", as the theory is
currently known, indeed found a positive correlation between the number of
legislature seats and government spending, although the effect was sometimes
limited to the lower house [e.g., @baqir1999districts;
@bradbury2001legislative; @gilligan1995deviations]. However, recent research
has questioned the validity of the theory. For instance, spending limits or
strong executives may reduce the inefficiency of pork barrel projects
[@chen_malhotra_2007; @primo2006stop]. Moreover, @primo2008distributive affirm
that, due to spatial spillovers, a collection of small districts can supply
public goods more efficiently than the central government. The authors conclude
that a "reverse law of $1/n$" may hold, wherein a higher number of legislators
in small constituencies decrease the overall public spending.
